---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---
```{r message=FALSE, warning=FALSE, include=FALSE}
#install.packages("PerformanceAnalytics")
library(quantmod)
library(PerformanceAnalytics)
symbols <- c("AAPL", "MSFT", "TSLA")
getSymbols(symbols, src = "yahoo", from = "2019-01-01", to = "2024-12-31")
```


• Which stock has the highest risk ?

In finance, risk is typically measured by the variability of asset prices over time. This variability, or volatility, is commonly quantified using the standard deviation of daily returns. In simple terms, the more daily returns fluctuate, the riskier the asset is considered to be.
Here, we present the comparison of standard deviations for our three assets, which allows us to assess and compare the variability of their daily returns. This provides a direct measure of the relative risk associated with each stock

```{r}
# Calculate daily returns
returns_aapl <- dailyReturn(Ad(AAPL))
returns_msft <- dailyReturn(Ad(MSFT))
returns_tsla <- dailyReturn(Ad(TSLA))
```


```{r}
# Calculate standard deviations
sd_aapl <- sd(returns_aapl)
sd_msft <- sd(returns_msft)
sd_tsla <- sd(returns_tsla)

# Print with labels
cat("Standard Deviation of AAPL:", sd_aapl, "\n")
cat("Standard Deviation of MSFT:", sd_msft, "\n")
cat("Standard Deviation of TSLA:", sd_tsla, "\n")
```

Tesla (TSLA) has the highest risk (volatility) among the three stocks, as it has the largest standard deviation of daily returns. Tesla's volatility is approximately twice that of Apple, indicating that fluctuations in Tesla's stock price could be twice as large compared to Apple's.

However, volatility alone does not capture the full picture of risk. It reflects short-term fluctuations but does not show how deep or prolonged a loss could be. Therefore, we continue our analysis by examining the Maximum Drawdown, which provides insight into the most severe loss an investor could have experienced during the observation period.

```{r}
mdd_aapl <- maxDrawdown(returns_aapl)
mdd_msft <- maxDrawdown(returns_msft)
mdd_tsla <- maxDrawdown(returns_tsla)

cat("Maximum Drawdown of AAPL:", mdd_aapl, "\n")
cat("Maximum Drawdown of MSFT:", mdd_msft, "\n")
cat("Maximum Drawdown of TSLA:", mdd_tsla, "\n")
```

The Maximum Drawdown results further confirm Tesla's high-risk profile. While Apple and Microsoft experienced drawdowns of approximately 31% and 37% respectively, Tesla's drawdown exceeded 73%. This indicates that during the worst observed period, Tesla investors could have faced a significantly deeper loss, highlighting the asset's vulnerability to extreme downturns. Historically, Tesla’s maximum drawdown has also been larger compared to Apple and Microsoft; according to one analysis, since 2010, Tesla stock has experienced a peak loss of around 61%, whereas Apple’s largest drawdown remained around 40%.


Although Maximum Drawdown reveals the magnitude of worst-case losses, it does not account for the efficiency of risk-taking over time. Therefore, to complement our understanding of risk, we consider the Sharpe Ratio—a key metric that relates return to volatility and provides insight into the quality of each asset's risk-adjusted performance.

The Sharpe Ratio is another key measure. It evaluates returns relative to the level of risk taken. It helps answer the crucial question for investors: "How much return am I getting for each unit of risk?"

```{r}
SharpeRatio(returns_aapl, Rf = 0)
SharpeRatio(returns_msft, Rf = 0)
SharpeRatio(returns_tsla, Rf = 0)
```
Across most risk measures, Apple delivers the best risk-adjusted returns, making it the most efficient investment among the three. While Tesla is more volatile, its performance under extreme conditions, particularly under Expected Shortfall and downside risk (SemiSD), is relatively strong.Tesla’nın Sharpe oranı beklenenden yüksek çıktı, çünkü incelenen dönemde olağanüstü getiri performansı göstererek yüksek volatilitesini telafi etti . Microsoft, on the other hand, shows the most conservative profile with consistently lower Sharpe Ratios


Lastly, we include Value at Risk (VaR), which serves as a financial weather forecast, indicating the probability of extreme losses ahead. While VaR tells us how much we could lose with a certain confidence level (e.g., 95%), it does not capture the severity of losses beyond that threshold. In this analysis, we use the variance-covariance method (also known as the parametric method), which assumes normally distributed returns.




```{r}
# Calculate Value at Risk (95%, Gaussian method)
var_aapl <- VaR(returns_aapl, p = 0.95, method = "gaussian")
var_msft <- VaR(returns_msft, p = 0.95, method = "gaussian")
var_tsla <- VaR(returns_tsla, p = 0.95, method = "gaussian")

# Print with labels
cat("95% VaR (Gaussian) of AAPL:", var_aapl, "\n")
cat("95% VaR (Gaussian) of MSFT:", var_msft, "\n")
cat("95% VaR (Gaussian) of TSLA:", var_tsla, "\n")
```

The Value at Risk (VaR) results align with the earlier volatility and drawdown findings. Tesla again exhibits the highest downside risk, with a potential daily loss of 6.4% at a 95% confidence level. Apple and Microsoft show significantly lower VaR values, reinforcing their relatively lower risk profiles. This is consistent with expectations, as Tesla’s price distribution has a wider variance, increasing the likelihood of large losses even if they are low-probability events. While VaR does not capture the full magnitude of extreme losses, it serves as an important indicator of short-term downside probability.

VaR provides a probabilistic estimate of potential losses, helping investors understand how much they might lose on a typical day under normal market conditions. However, it does not account for rare but extreme losses (‘black swan’ events). Therefore, VaR should be used alongside other risk measures, such as Maximum Drawdown and Sharpe Ratio, to get a more complete picture of an asset’s risk profile.”

Together with the Sharpe Ratio and Maximum Drawdown, the VaR analysis completes our risk profile comparison. Each metric highlights a different facet of risk—volatility, worst-case loss, efficiency, and probability of loss—and together they offer a comprehensive view of how each asset behaves under uncertainty.

•	Which stock had the highest average return?

Measuring return is a fundamental step in evaluating investment performance. However, the chosen calculation method can significantly influence investors’ interpretations of these results. Two commonly used methods are the arithmetic mean return and the geometric mean return, each with its advantages and limitations. The appropriate method should be selected based on the purpose and context of the analysis.

When looking at the returns for my investment portfolio, should I use arithmetic or geometric returns?

And here’s the response we got from ChatGPT:

When analyzing investment returns, both arithmetic and geometric returns have their uses, and it ultimately depends on the context and the purpose of your analysis.

The arithmetic mean is calculated by adding up all daily or annual returns over a period and dividing the total by the number of observations. Due to its simplicity, it is widely used for short-term performance comparisons and return estimates.


```{r}
mean_return_aapl <- mean(returns_aapl)
mean_return_msft <- mean(returns_msft)
mean_return_tsla <- mean(returns_tsla)

cat("Average Return of Apple:", mean_return_aapl, "\n")
cat("Average Return of Microsoft:", mean_return_msft, "\n")
cat("Average Return of Tesla:", mean_return_tsla, "\n")

```

The geometric mean, on the other hand, accounts for the effects of compounding and provides a more realistic measure of long-term investment performance. This method reflects the cumulative effect of returns over time and is generally more reliable for long-term evaluations.

According to an analysis published by TheStreet, the arithmetic mean may be preferable for short-term estimates, while the geometric mean offers a more realistic view for long-term performance, especially in volatile market conditions.

```{r}
geo_mean_aapl <- prod(1 + returns_aapl)^(1 / length(returns_aapl)) - 1

geo_mean_msft <- prod(1 + returns_msft)^(1 / length(returns_msft)) - 1

geo_mean_tsla <- prod(1 + returns_tsla)^(1 / length(returns_tsla)) - 1

cat("Geometric Mean Return of Apple:", geo_mean_aapl, "\n")
cat("Geometric Mean Return of Microsoft:", geo_mean_msft, "\n")
cat("Geometric Mean Return of Tesla:", geo_mean_tsla, "\n")

```

A Closer Look at the Results

```{r}
cat("+-----------+------------------+------------------+\n")
cat("| Stock     | Arithmetic Mean   | Geometric Mean    |\n")
cat("+-----------+------------------+------------------+\n")
cat("| Apple     | 0.001448724       | 0.001260127       |\n")
cat("| Microsoft | 0.00115778        | 0.0009909139      |\n")
cat("| Tesla     | 0.002814698       | 0.001993475       |\n")
cat("+-----------+------------------+------------------+\n")

```

As the results show, Tesla achieved the highest performance based on both the arithmetic and geometric average returns.

Tesla has faced more challenges than most companies. However, under Elon Musk’s leadership, Tesla has turned the vision of electric vehicles into reality. This achievement pushed Tesla’s market value beyond $1 trillion, making Musk, one of its largest shareholders, one of the richest individuals in the world.

🍏 Apple – A Symbol of Long-Term Stability and Growth

Apple is not only one of the largest tech companies but also one of the most successful companies in history. Under Steve Jobs’ leadership, products such as Mac computers, iPods, and iPhones changed the world. However, trust in Apple’s stock was not always high.

In 2002, Apple’s share price dropped below $0.10, leading many investors to consider it worthless.

Nevertheless, Apple delivered extraordinary growth, achieving a total return of 154,000% and making history. This milestone was reached when Apple’s share price hit an all-time high in January 2022, rewarding long-term investors with exceptional gains.

Today, Apple remains a symbol of reliable, long-term growth, maintaining its position in portfolios as a balanced investment option with moderate risk and stable returns.

---------------------------------------

•	Does diversification reduce risk?

There is a well-known saying often attributed to economist Harry Markowitz, the father of Modern Portfolio Theory:

“Diversification is the only free lunch in investing.”

Or, as people like to put it more casually: “Don’t put all your eggs in one basket.”

Diversification means spreading investments across different assets to reduce exposure to the risk of any single investment. The basic idea is that not all assets move in the same direction at the same time. By combining assets with different risk and return profiles, investors can potentially reduce the overall risk of their portfolio while maintaining reasonable return expectations.

The goal of diversification is to reduce overall volatility and achieve a more balanced return by combining assets with low correlation.
Correlation analysis is conducted to identify which assets, when combined in a portfolio, will have a risk-reducing effect.

Low correlation reduces portfolio volatility.
High correlation increases portfolio volatility.

```{r echo=FALSE, message=TRUE}
prices <- merge(Cl(AAPL), Cl(TSLA), Cl(MSFT))
colnames(prices) <- c("AAPL", "TSLA", "MSFT")
returns <- na.omit(ROC(prices, type = "discrete"))
cor_matrix <- cor(returns)
print(cor_matrix)

```

AAPL – TSLA = 0.47
A moderate positive relationship. Sometimes they move together, sometimes they don’t.

AAPL – MSFT = 0.73
A strong positive relationship. They generally move in the same direction.

TSLA – MSFT = 0.43
A moderate relationship. Sometimes they move similarly, but there is also a degree of independence.

We will use these results to build our portfolio diversification strategy.
Assets with very high correlation (such as AAPL and MSFT) provide less diversification.

Assets with moderate or low correlation (such as TSLA and AAPL or TSLA and MSFT) provide better diversification.

The goal is to determine whether the assets added to the portfolio balance each other or tend to move in the same direction.

Our hypothesis is as follows:

Low Risk / Stability Objective:
A portfolio weighted 50% Microsoft and 50% Apple is expected to provide stable but limited returns due to its low volatility.

Balanced Risk / Return Objective:
A portfolio weighted 50% Microsoft, 30% Apple, and 20% Tesla is expected to offer moderate returns with an acceptable level of risk.

High Return / High Risk Objective:
A portfolio weighted 50% Tesla, 25% Apple, and 25% Microsoft is expected to deliver the highest potential returns, despite higher volatility.

Maximum Sharpe Ratio Objective:
A portfolio weighted 85% Microsoft and 15% Tesla is expected to provide the highest return per unit of risk, maximizing the Sharpe Ratio.

```{r}
portfolio_analysis <- function(weights, returns, name) {
  mean_ret <- colMeans(returns) * 252
  cov_matrix <- cov(returns) * 252
  port_return <- sum(weights * mean_ret)
  port_variance <- t(weights) %*% cov_matrix %*% weights
  port_volatility <- sqrt(port_variance)
  port_sharpe <- port_return / port_volatility
  
  cat("\n====", name, "====\n")
  cat("Annual Return: ", round(port_return * 100, 2), "%\n")
  cat("Annual Volatility: ", round(port_volatility * 100, 2), "%\n")
  cat("Sharpe Ratio: ", round(port_sharpe, 2), "\n")
}

# Portfolio Scenarios
portfolio_analysis(c(0.50, 0.00, 0.50), returns, "Low Risk / Stability")
portfolio_analysis(c(0.30, 0.20, 0.50), returns, "Balanced Risk / Return")
portfolio_analysis(c(0.25, 0.50, 0.25), returns, "High Return / High Risk")
portfolio_analysis(c(0.00, 0.15, 0.85), returns, "Maximum Sharpe Ratio")

```

Balanced Portfolio (50% MSFT – 30% AAPL – 20% TSLA)
Achieved the highest Sharpe ratio of 1.28, with an annual return of 39% and volatility of 30.5%. This represents the best balance between risk and return.

Low-Risk Portfolio (50% MSFT – 50% AAPL)
Stands out as the least risky option, offering a 32% annual return with relatively low volatility.

High-Return Portfolio (50% TSLA – 25% AAPL – 25% MSFT)
Provides the highest potential return of 51.5% annually, but comes with high volatility of 40.8%, making it susceptible to significant fluctuations.

Maximum Sharpe Portfolio (85% MSFT – 15% TSLA)
Appears theoretically efficient, but does not outperform the balanced portfolio in practice.

Recommendation
We recommend the 50% MSFT – 30% AAPL – 20% TSLA allocation as the optimal choice for investors seeking a strong balance between risk and return, supported by the best Sharpe ratio.

For risk-averse investors, the 50% MSFT – 50% AAPL portfolio is suggested.

For aggressive investors, the 50% TSLA-weighted portfolio could be considered, acknowledging its higher volatility.

*Impact of Portfolio Returns on Individual Stocks*

Identifying Key Drivers: Regression analysis helps determine which stock has the greatest influence on overall portfolio movements.

Measuring Sensitivity: It quantifies how sensitive each stock is to changes in the portfolio, using the beta coefficient as a measure of this sensitivity.

Assessing Diversification: It provides insights into whether the portfolio benefits from true diversification or if certain stocks dominate the portfolio’s risk and return dynamics.

```{r}
weights <- c(0.30, 0.20, 0.50)  # AAPL, TSLA, MSFT

# Portföy getirisi
portfolio_returns <- returns_aapl * 0.30 + returns_tsla * 0.20 + returns_msft * 0.50

lm(returns_aapl ~ portfolio_returns)
lm(returns_tsla ~ portfolio_returns)
lm(returns_msft ~ portfolio_returns)

```


Tesla is the most influential stock in driving portfolio movements, with a beta greater than 1.6.

Apple and Microsoft help stabilize the portfolio with their lower volatility.

The primary source of risk is Tesla, but it also offers the highest return potential.

This structure clearly demonstrates effective diversification, highlighting Tesla as the main driver of risk.

To reduce overall portfolio risk, one could lower the Tesla weighting while maintaining diversification.



```{r}
print_regression_summary <- function(stock_name, stock_returns, portfolio_returns) {
  model <- lm(stock_returns ~ portfolio_returns)
  model_summary <- summary(model)
  model_confint <- confint(model)
  
  beta <- model_summary$coefficients[2, 1]
  t_value <- model_summary$coefficients[2, 3]
  p_value <- model_summary$coefficients[2, 4]
  conf_low <- model_confint[2, 1]
  conf_high <- model_confint[2, 2]
  r_squared <- model_summary$r.squared * 100
  
  cat("========================================\n")
  cat("        REGRESSION SUMMARY -", stock_name, "\n")
  cat("========================================\n")
  cat(sprintf("%-25s: %.4f\n", "Beta", beta))
  cat(sprintf("%-25s: %.2f\n", "t-value", t_value))
  cat(sprintf("%-25s: %.4g\n", "p-value", p_value))
  cat(sprintf("%-25s: [%.4f , %.4f]\n", "95% Confidence Interval", conf_low, conf_high))
  cat(sprintf("%-25s: %.2f%%\n", "R-squared", r_squared))
  cat("========================================\n\n")
}

weights <- c(0.30, 0.20, 0.50)
portfolio_returns <- returns_aapl * weights[1] + returns_tsla * weights[2] + returns_msft * weights[3]

print_regression_summary("AAPL", returns_aapl, portfolio_returns)
print_regression_summary("TSLA", returns_tsla, portfolio_returns)
print_regression_summary("MSFT", returns_msft, portfolio_returns)

```
The table above clearly presents the influence of AAPL, TSLA, and MSFT on the portfolio returns, along with the statistical reliability of these effects.

AAPL and MSFT show strong and statistically significant relationships with the portfolio returns. Their beta values, around 0.85-0.86, indicate that these stocks contribute stabilizing effects to the portfolio’s performance. MSFT, in particular, stands out with the highest explanatory power (77.46%), making it the most aligned stock with the portfolio performance.

TSLA, with a high beta of 1.62, is identified as the most influential stock in driving portfolio movements. This highlights TSLA's high volatility and risk, but also its high return potential. However, its lower R² (59.11%) compared to AAPL and MSFT suggests that TSLA carries additional, less predictable risk factors beyond the portfolio’s general movements.

All results are highly statistically significant (p < 0.001), and the narrow and positive confidence intervals further confirm the robustness and reliability of the estimates.


This table demonstrates that MSFT and AAPL act as stabilizers, contributing to portfolio consistency, while TSLA drives both risk and return dynamics.
For a balanced portfolio, the weight of TSLA should be carefully managed to control overall risk, while AAPL and MSFT provide stable and reliable performance contributions.


--------------------------------------------------------------------------------
Diversification means spreading investments across different assets to reduce exposure to the risk of any single investment. The basic idea is that not all assets move in the same direction at the same time. By combining assets with different risk and return profiles, investors can potentially reduce the overall risk of their portfolio while maintaining reasonable return expectations. That's why it's common to spread your investment in different field. One of the most popular ratio is 40/40/20 - 40% in solid asset like gold or bonds,which has low risk. 40% - ETF's with low-median parameter of risk and reasonable returns (8% per year approx) and 20% individual stocks, which will lead to high returns but also higher risk. "Good to know, ETF's (S&P500, for example), has 500 stock companies as a bundle. Recently, NVIDIA increased a lot in value, which drove the S&P500 way above. But, the risk measures are the same. That means, we benefit a lot from the cases like this, but if company goes bankrupt - it will not affect your portfolio significantly. It's brilliant" - Leave if you like Kuzu

We can prove this by calculating standard deviation both for diversified investment and single one and compare them. As we know, standard deviation considered to be a "Risk Marker", so we expect diversified portfolio to have lower standard deviation score.


```{r}

portfolio_returns <- (returns_aapl + returns_msft + returns_tsla) / 3

cat("Standard Deviation of AAPL:", sd(returns_aapl), "\n")
cat("Standard Deviation of MSFT:", sd(returns_msft), "\n")
cat("Standard Deviation of TSLA:", sd(returns_tsla), "\n")
cat("Standard Deviation of Diversified Portfolio:", sd(portfolio_returns), "\n")
```
As you can see, our diversified portfolio has 2% of Standard Deviation, meanwhile, AAPL and MSFT have 1.94% and 1.83% respectively. That means 2 things. 1 - I was wrong, Standard deviation of our portfolio is higher. 2 - AAPL and MSFT itself more safe asset to have. 

Why then Mr. Markowitz was so desperate about diversification? 
And the answer is - return. Let me explain.

When we combine these three stocks into an equally weighted diversified portfolio, the portfolio’s standard deviation is 2.17%, which is lower than Tesla’s individual risk, but slightly higher than Apple’s or Microsoft’s risk.

This result demonstrates that diversification reduces the overall impact of the riskiest asset in the portfolio. Even though the portfolio still carries some risk, the extreme fluctuations of Tesla are balanced out by the relative stability of Apple and Microsoft.

Moreover, the potential return of the diversified portfolio remains attractive, since it still benefits from Tesla’s higher return potential while reducing its extreme downside risk.

Therefore, this example illustrates why diversification makes sense in practice: it helps to lower risk while preserving opportunities for higher returns.

Is simple terms, as we want our portfolio to grow, we can invest in risky assets to gain more and still consider our portfolio to be safe, using diversification.

Let me demonstrate it, using the following chart:


```{r}

library(ggplot2)
library(tidyr)
library(scales)  # для форматирования в проценты

# Преобразуем данные
metrics_long <- metrics %>%
  pivot_longer(cols = c(Mean_Return, Standard_Deviation),
               names_to = "Metric", values_to = "Value")

# Bar Plot с процентами
ggplot(metrics_long, aes(x = Asset, y = Value, fill = Metric)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6) +
  geom_text(aes(label = scales::percent(Value, accuracy = 0.01)),
            position = position_dodge(width = 0.7),
            vjust = -0.5, size = 4) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.01)) +
  scale_fill_manual(values = c("Mean_Return" = "steelblue", "Standard_Deviation" = "tomato")) +
  labs(title = "Risk & Return Comparison by Asset",
       x = "",
       y = "Percentage",
       fill = "Metric") +
  theme_minimal(base_size = 14) +
  theme(legend.position = "top")
```
The Risk-Return Comparison chart illustrates how diversification helps to balance risk and return.

We can see that Tesla provides the highest average return (0.28%) but comes with the highest risk (4.06% standard deviation). On the other hand, Apple and Microsoft offer lower risk (around 1.8–1.9%) but also lower returns (around 0.11–0.14%).

The diversified portfolio, which combines all three stocks equally, achieves a higher return (0.18%) than Apple and Microsoft individually, while maintaining a moderate risk (2.17%), significantly lower than Tesla’s standalone risk.

This shows that diversification allows us to benefit from the growth potential of riskier assets like Tesla while keeping the overall risk at an acceptable level thanks to the stabilizing effect of safer assets like Apple and Microsoft.

In other words, diversification does not eliminate risk entirely, but it smooths the extremes, providing a more balanced and resilient portfolio that preserves the opportunity for higher returns without fully exposing the investor to the risks of any single stock.

To strengthen the analysis, we conducted two additional statistical tests:
	•	T-Test: This test was used to check whether the difference in returns between Tesla and Apple is statistically significant. The results confirmed that Tesla’s returns are not significantly higher than Apple’s, with a p-value above 0.05, supporting the conclusion that Tesla offers nearly same potential returns but at a higher risk.(Askim, please check. Maybe I calculated it wrong. It shouldn't be the same)
	
	
```{r}
t_test_result <- t.test(as.vector(returns_tsla), as.vector(returns_aapl))
print(t_test_result)
```

--------------------------------------------------------------------	












	
	
--------------------------------------------------------------------	
	
	•	Linear Regression: A regression analysis between Tesla’s returns and the diversified portfolio’s returns revealed a positive relationship. This indicates that Tesla’s performance has a measurable influence on the portfolio’s overall return, contributing to both its higher return and higher volatility. This supports the idea that adding a riskier asset like Tesla can boost portfolio performance while still maintaining a balanced risk profile thanks to diversification.
	
```{r}
# Линейная регрессия доходности Tesla против доходности портфеля
regression_model <- lm(returns_tsla ~ portfolio_returns)

# Вывод результата
summary(regression_model)
```

The linear regression results show a strong and statistically significant positive relationship between the returns of Tesla and the returns of the diversified portfolio.

Since the p-value is nearly 0, the probability of the result being an accident is extremely low. We can trust the result.

The coefficient of 1.65 indicates that Tesla’s returns amplify the portfolio’s movements, meaning Tesla behaves like a high-beta asset, increasing portfolio returns when the portfolio performs well, but also increasing losses when the portfolio performs poorly (higher volatility). That means that when our portfolio grows 1%, Tesla grows 1.65%.

With an R-squared of 77.8%, the model explains a large portion of Tesla’s return variability, confirming that Tesla’s performance is closely related to the portfolio’s overall dynamics. This reinforces the idea that adding Tesla to a diversified portfolio can boost returns, but it also makes the portfolio more sensitive to market movements.
⸻



---
https://www.thestreet.com/apple/stock/apple-vs-tesla-which-growth-stock-to-own#:~:text=Apple%20vs,vs.%20AAPL%27s%2040

---
https://www.thestreet.com/apple/stock/apple-vs-tesla-which-growth-stock-to-own#:~:text=Apple%20vs,vs.%20AAPL%27s%2040

https://www.investopedia.com/articles/investing/071113/breaking-down-geometric-mean.asp

https://www.thestreet.com/retirement-daily/your-money/testing-chatgpt-arithmetic-vs-geometric-returns

---

https://corporatefinanceinstitute.com/resources/career-map/sell-side/capital-markets/harry-markowitz/

