---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---
```{r message=FALSE, warning=FALSE, include=FALSE}
#install.packages("PerformanceAnalytics")
library(quantmod)
library(PerformanceAnalytics)
library(ggplot2)
library(dplyr)
library(lubridate)
library(scales)
symbols <- c("AAPL", "MSFT", "TSLA")
getSymbols(symbols, src = "yahoo", from = "2019-01-01", to = "2024-12-31")
```

```{r include=FALSE}
returns_aapl <- dailyReturn(Ad(AAPL))
returns_msft <- dailyReturn(Ad(MSFT))
returns_tsla <- dailyReturn(Ad(TSLA))
```

• Which stock has the highest risk ?

Volatility is a frequently encountered concept in the world of finance and holds great importance for investors. But what exactly is volatility? Volatility refers to the degree of fluctuation in the price of a financial asset. In other words, it describes how quickly and significantly the price of an asset changes. For investors, volatility can imply risk and uncertainty, but when managed with the right strategies, it can also present opportunities.

In volatility, which measures the price fluctuations of an asset, sudden and large changes in stock prices indicate high volatility. On the other hand, low volatility means that prices are more stable and predictable. Volatility plays a critical role in helping investors determine their risk tolerance and adjust their portfolios accordingly.

There are several ways to measure volatility, but the most common method is the calculation of standard deviation. Standard deviation indicates how much an asset’s return deviates from its average. A high standard deviation signifies high volatility, while a low standard deviation indicates low volatility.

High volatility is often observed during periods of increased uncertainty and risk in the markets. During such times, prices can experience sudden and significant changes, which may amplify both potential gains and losses. Investors should closely monitor market movements during high-volatility periods and rebalance their portfolios if necessary. High volatility typically arises due to factors such as economic uncertainty, political events, natural disasters, or major company-specific developments.

Our data spans from 2019 to 2024, a period marked by major global events that likely influenced market volatility. These include the COVID-19 pandemic (2020), vaccine-driven recovery (2021), the Russia-Ukraine war (2022), global inflation and interest rate hikes (2022–2023), the AI stock rally (2023), and political and economic uncertainty in 2024. These events should be considered when interpreting volatility and asset performance.

To examine these effects more closely, we will use the volatility graph. This will allow us to compare the daily return variability of Apple, Microsoft, and Tesla more accurately, and better understand how each stock responded to market events during the 2019–2024 period.

```{r}
returns_combined <- merge(returns_aapl, returns_msft, returns_tsla)
colnames(returns_combined) <- c("AAPL", "MSFT", "TSLA")
returns_df <- data.frame(Date = index(returns_combined),
                         coredata(returns_combined))
returns_df <- returns_df %>%
  mutate(HalfYear = paste0(year(Date), " H", ifelse(month(Date) <= 6, 1, 2)))

grouped_data <- returns_df %>%
  group_by(HalfYear) %>%
  summarise(across(c(AAPL, MSFT, TSLA),
                   list(Mean = ~mean(.x, na.rm = TRUE),
                        SD = ~sd(.x, na.rm = TRUE))))


```


```{r}
grouped_data$HalfYear <- factor(grouped_data$HalfYear, levels = grouped_data$HalfYear)

event_labels <- data.frame(
  HalfYear = c("2020 H1", "2021 H1", "2022 H1", "2022 H2", "2023 H1"),
  label = c("COVID", "Vaccine", "War", "Inflation", "AI")
)

ggplot(grouped_data, aes(x = HalfYear)) +
  geom_point(aes(y = AAPL_SD, color = "AAPL"), size = 3) +
  geom_point(aes(y = MSFT_SD, color = "MSFT"), size = 3) +
  geom_point(aes(y = TSLA_SD, color = "TSLA"), size = 3) +
  geom_line(aes(y = AAPL_SD, group = 1, color = "AAPL")) +
  geom_line(aes(y = MSFT_SD, group = 2, color = "MSFT")) +
  geom_line(aes(y = TSLA_SD, group = 3, color = "TSLA")) +
  geom_vline(xintercept = which(grouped_data$HalfYear %in% event_labels$HalfYear),
             linetype = "dashed", color = "red", size = 0.6) +
  geom_text(data = event_labels,
            aes(x = HalfYear, y = 0, label = label),
            inherit.aes = FALSE,
            angle = 0, vjust = 1.5, hjust = 0.5, color = "red", size = 3.5) +
  labs(title = "6-Month Volatility (Standard Deviation) and Key Events",
       subtitle = "Periodical volatility comparison of AAPL, MSFT, and TSLA",
       x = "Period (Half-Year)",
       y = "Standard Deviation (Volatility)",
       color = "Stock") +
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```


Between 2019 and 2024, the 6-month volatility trends of AAPL, MSFT, and TSLA reveal how major global events impacted market stability. During the first half of 2020, at the onset of the COVID-19 pandemic, all three stocks experienced a significant increase in volatility, with TSLA showing the most pronounced spike. As vaccines became available in the first half of 2021, market confidence returned and volatility decreased notably across all three stocks.

In 2022, the outbreak of the Russia–Ukraine war and rising global inflation led to another wave of volatility, particularly affecting AAPL and TSLA, while MSFT remained relatively stable. By the first half of 2023, despite the surge in AI-driven market optimism, volatility declined further for AAPL and MSFT, whereas TSLA maintained a consistently higher risk profile.

Throughout the period, MSFT exhibited the most stable and defensive behavior, AAPL responded moderately to global shifts, and TSLA stood out with the highest and most persistent volatility, reflecting its sensitivity to both macroeconomic shocks and speculative dynamics.

While volatility shows how much returns fluctuate, it does not capture the depth or duration of losses. To address this, we examine the Maximum Drawdown (MDD), which measures the largest decline from a peak to a trough over the entire period. It reflects the most severe loss an investor could have faced.


```{r echo=FALSE}
mdd_aapl <- maxDrawdown(returns_aapl)
mdd_msft <- maxDrawdown(returns_msft)
mdd_tsla <- maxDrawdown(returns_tsla)

cat("Maximum Drawdown of AAPL:", mdd_aapl, "\n")
cat("Maximum Drawdown of MSFT:", mdd_msft, "\n")
cat("Maximum Drawdown of TSLA:", mdd_tsla, "\n")
```

The Maximum Drawdown results further confirm Tesla's high-risk profile. While Apple and Microsoft experienced drawdowns of approximately 31% and 37% respectively, Tesla's drawdown exceeded 73%. This indicates that during the worst observed period, Tesla investors could have faced a significantly deeper loss, highlighting the asset's vulnerability to extreme downturns.

Historically, Tesla’s maximum drawdown has also been larger compared to Apple and Microsoft; according to one analysis, since 2010, Tesla stock has experienced a peak loss of around 61%, whereas Apple’s largest drawdown remained around 40%.

However, in finance, risk does not simply mean danger—it also represents opportunity. Higher risk can imply greater return potential, which is why many investors are still attracted to stocks like TSLA despite their volatility and drawdown profiles.

•	Which stock had the highest average return?

Two commonly used methods are the arithmetic mean return and the geometric mean return, each with its advantages and limitations. The appropriate method should be selected based on the purpose and context of the analysis.

When looking at the returns for my investment portfolio, should I use arithmetic or geometric returns?

And here’s the response we got from ChatGPT:

When analyzing investment returns, both arithmetic and geometric returns have their uses, and it ultimately depends on the context and the purpose of your analysis.

The arithmetic mean is calculated by adding up all daily or annual returns over a period and dividing the total by the number of observations. Due to its simplicity, it is widely used for short-term performance comparisons and return estimates.


```{r}
grouped_data$HalfYear <- factor(grouped_data$HalfYear, levels = grouped_data$HalfYear)

event_labels <- data.frame(
  HalfYear = c("2020 H1", "2021 H1", "2022 H1", "2022 H2", "2023 H1"),
  label = c("COVID", "Vaccine", "War", "Inflation", "AI")
)

ggplot(grouped_data, aes(x = HalfYear)) +
  geom_line(aes(y = AAPL_Mean, color = "AAPL"), group = 1, size = 1) +
  geom_line(aes(y = MSFT_Mean, color = "MSFT"), group = 2, size = 1) +
  geom_line(aes(y = TSLA_Mean, color = "TSLA"), group = 3, size = 1) +
  geom_point(aes(y = AAPL_Mean, color = "AAPL"), size = 2) +
  geom_point(aes(y = MSFT_Mean, color = "MSFT"), size = 2) +
  geom_point(aes(y = TSLA_Mean, color = "TSLA"), size = 2) +
  geom_hline(yintercept = 0, linetype = "dotted", color = "black") +
  geom_vline(xintercept = which(grouped_data$HalfYear %in% event_labels$HalfYear),
             linetype = "dashed", color = "red", size = 0.5) +
  geom_text(data = event_labels,
            aes(x = HalfYear, y = 0, label = label),
            inherit.aes = FALSE,
            angle = 0, vjust = 1.5, hjust = 0.5, color = "red", size = 3.5) +
  labs(title = "6-Month Average Returns by Stock with Key Events",
       x = "Period (Half-Year)",
       y = "Average Daily Return",
       color = "Stock") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(labels = scales::percent)
  

```

The geometric mean, on the other hand, accounts for the effects of compounding and provides a more realistic measure of long-term investment performance. This method reflects the cumulative effect of returns over time and is generally more reliable for long-term evaluations.

According to an analysis published by TheStreet, the arithmetic mean may be preferable for short-term estimates, while the geometric mean offers a more realistic view for long-term performance, especially in volatile market conditions.


```{r}
geo_mean <- function(x) {
  prod(1 + x)^(1/length(x)) - 1
}

geo_data <- returns_df %>%
  group_by(HalfYear) %>%
  summarise(
    AAPL_Geo = geo_mean(AAPL),
    MSFT_Geo = geo_mean(MSFT),
    TSLA_Geo = geo_mean(TSLA)
  )

```



```{r}
ggplot(grouped_data, aes(x = HalfYear)) +
  geom_line(aes(y = AAPL_Geo, color = "AAPL"), size = 1) +
  geom_line(aes(y = MSFT_Geo, color = "MSFT"), size = 1) +
  geom_line(aes(y = TSLA_Geo, color = "TSLA"), size = 1) +
  geom_point(aes(y = AAPL_Geo, color = "AAPL"), size = 2) +
  geom_point(aes(y = MSFT_Geo, color = "MSFT"), size = 2) +
  geom_point(aes(y = TSLA_Geo, color = "TSLA"), size = 2) +
  geom_hline(yintercept = 0, linetype = "dotted", color = "black") +
  geom_vline(xintercept = which(grouped_data$HalfYear %in% event_labels$HalfYear),
             linetype = "dashed", color = "red", size = 0.5) +
  geom_text(data = event_labels,
            aes(x = HalfYear, y = 0, label = label),
            inherit.aes = FALSE,
            vjust = 1.5, hjust = 0.5, color = "red", size = 3.5) +
  labs(title = "6-Month Geometric Average Returns by Stock with Key Events",
       x = "Period (Half-Year)",
       y = "Geometric Average Daily Return",
       color = "Stock") +
  scale_y_continuous(labels = percent) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

A Closer Look at the Results

```{r}
cat("+-----------+------------------+------------------+\n")
cat("| Stock     | Arithmetic Mean   | Geometric Mean    |\n")
cat("+-----------+------------------+------------------+\n")
cat("| Apple     | 0.001448724       | 0.001260127       |\n")
cat("| Microsoft | 0.00115778        | 0.0009909139      |\n")
cat("| Tesla     | 0.002814698       | 0.001993475       |\n")
cat("+-----------+------------------+------------------+\n")

```

As the results show, Tesla achieved the highest performance based on both the arithmetic and geometric average returns.

Tesla has faced more challenges than most companies. However, under Elon Musk’s leadership, Tesla has turned the vision of electric vehicles into reality. This achievement pushed Tesla’s market value beyond $1 trillion, making Musk, one of its largest shareholders, one of the richest individuals in the world.

🍏 Apple – A Symbol of Long-Term Stability and Growth

Apple is not only one of the largest tech companies but also one of the most successful companies in history. Under Steve Jobs’ leadership, products such as Mac computers, iPods, and iPhones changed the world. However, trust in Apple’s stock was not always high.

In 2002, Apple’s share price dropped below $0.10, leading many investors to consider it worthless.

Nevertheless, Apple delivered extraordinary growth, achieving a total return of 154,000% and making history. This milestone was reached when Apple’s share price hit an all-time high in January 2022, rewarding long-term investors with exceptional gains.

Today, Apple remains a symbol of reliable, long-term growth, maintaining its position in portfolios as a balanced investment option with moderate risk and stable returns.

---------------------------------------

•	Does diversification reduce risk?

There is a well-known saying often attributed to economist Harry Markowitz, the father of Modern Portfolio Theory:

“Diversification is the only free lunch in investing.”

Or, as people like to put it more casually: “Don’t put all your eggs in one basket.”

Diversification means spreading investments across different assets to reduce exposure to the risk of any single investment. The basic idea is that not all assets move in the same direction at the same time. By combining assets with different risk and return profiles, investors can potentially reduce the overall risk of their portfolio while maintaining reasonable return expectations.

The goal of diversification is to reduce overall volatility and achieve a more balanced return by combining assets with low correlation.
Correlation analysis is conducted to identify which assets, when combined in a portfolio, will have a risk-reducing effect.

Low correlation reduces portfolio volatility.
High correlation increases portfolio volatility.

```{r echo=FALSE, message=TRUE}
prices <- merge(Cl(AAPL), Cl(TSLA), Cl(MSFT))
colnames(prices) <- c("AAPL", "TSLA", "MSFT")
returns <- na.omit(ROC(prices, type = "discrete"))
cor_matrix <- cor(returns)
print(cor_matrix)

```

AAPL – TSLA = 0.47
A moderate positive relationship. Sometimes they move together, sometimes they don’t.

AAPL – MSFT = 0.73
A strong positive relationship. They generally move in the same direction.

TSLA – MSFT = 0.43
A moderate relationship. Sometimes they move similarly, but there is also a degree of independence.

We will use these results to build our portfolio diversification strategy.
Assets with very high correlation (such as AAPL and MSFT) provide less diversification.

Assets with moderate or low correlation (such as TSLA and AAPL or TSLA and MSFT) provide better diversification.

The goal is to determine whether the assets added to the portfolio balance each other or tend to move in the same direction.

Our hypothesis is as follows:

Low Risk / Stability Objective:
A portfolio weighted 50% Microsoft and 50% Apple is expected to provide stable but limited returns due to its low volatility.

Balanced Risk / Return Objective:
A portfolio weighted 50% Microsoft, 30% Apple, and 20% Tesla is expected to offer moderate returns with an acceptable level of risk.

High Return / High Risk Objective:
A portfolio weighted 50% Tesla, 25% Apple, and 25% Microsoft is expected to deliver the highest potential returns, despite higher volatility.

Maximum Sharpe Ratio Objective:
A portfolio weighted 85% Microsoft and 15% Tesla is expected to provide the highest return per unit of risk, maximizing the Sharpe Ratio.

```{r}
portfolio_analysis <- function(weights, returns, name) {
  mean_ret <- colMeans(returns) * 252
  cov_matrix <- cov(returns) * 252
  port_return <- sum(weights * mean_ret)
  port_variance <- t(weights) %*% cov_matrix %*% weights
  port_volatility <- sqrt(port_variance)
  port_sharpe <- port_return / port_volatility
  
  cat("\n====", name, "====\n")
  cat("Annual Return: ", round(port_return * 100, 2), "%\n")
  cat("Annual Volatility: ", round(port_volatility * 100, 2), "%\n")
  cat("Sharpe Ratio: ", round(port_sharpe, 2), "\n")
}

# Portfolio Scenarios
portfolio_analysis(c(0.50, 0.00, 0.50), returns, "Low Risk / Stability")
portfolio_analysis(c(0.30, 0.20, 0.50), returns, "Balanced Risk / Return")
portfolio_analysis(c(0.25, 0.50, 0.25), returns, "High Return / High Risk")
portfolio_analysis(c(0.00, 0.15, 0.85), returns, "Maximum Sharpe Ratio")

```

Balanced Portfolio (50% MSFT – 30% AAPL – 20% TSLA)
Achieved the highest Sharpe ratio of 1.28, with an annual return of 39% and volatility of 30.5%. This represents the best balance between risk and return.

Low-Risk Portfolio (50% MSFT – 50% AAPL)
Stands out as the least risky option, offering a 32% annual return with relatively low volatility.

High-Return Portfolio (50% TSLA – 25% AAPL – 25% MSFT)
Provides the highest potential return of 51.5% annually, but comes with high volatility of 40.8%, making it susceptible to significant fluctuations.

Maximum Sharpe Portfolio (85% MSFT – 15% TSLA)
Appears theoretically efficient, but does not outperform the balanced portfolio in practice.

Recommendation
We recommend the 50% MSFT – 30% AAPL – 20% TSLA allocation as the optimal choice for investors seeking a strong balance between risk and return, supported by the best Sharpe ratio.

For risk-averse investors, the 50% MSFT – 50% AAPL portfolio is suggested.

For aggressive investors, the 50% TSLA-weighted portfolio could be considered, acknowledging its higher volatility.

*Impact of Portfolio Returns on Individual Stocks*

Identifying Key Drivers: Regression analysis helps determine which stock has the greatest influence on overall portfolio movements.

Measuring Sensitivity: It quantifies how sensitive each stock is to changes in the portfolio, using the beta coefficient as a measure of this sensitivity.

Assessing Diversification: It provides insights into whether the portfolio benefits from true diversification or if certain stocks dominate the portfolio’s risk and return dynamics.

```{r}
weights <- c(0.30, 0.20, 0.50)  # AAPL, TSLA, MSFT

# Portföy getirisi
portfolio_returns <- returns_aapl * 0.30 + returns_tsla * 0.20 + returns_msft * 0.50

lm(returns_aapl ~ portfolio_returns)
lm(returns_tsla ~ portfolio_returns)
lm(returns_msft ~ portfolio_returns)

```


The regression results confirm that Tesla (TSLA) is the most influential stock in explaining portfolio movements, with a beta greater than 1.6, indicating high sensitivity to portfolio changes.

Apple (AAPL) and Microsoft (MSFT) both show lower beta values (around 0.85), suggesting that they help stabilize the portfolio by contributing steady returns with lower volatility.

While Tesla represents the primary source of portfolio risk, it also offers the highest return potential.

Overall, the results demonstrate that the portfolio achieves effective diversification, but Tesla dominates the risk profile.

To better manage overall portfolio risk, reducing the weight of Tesla could be considered, while keeping Apple and Microsoft as stabilizing components to maintain diversification benefits.



```{r}
print_regression_summary <- function(stock_name, stock_returns, portfolio_returns) {
  model <- lm(stock_returns ~ portfolio_returns)
  model_summary <- summary(model)
  model_confint <- confint(model)
  
  beta <- model_summary$coefficients[2, 1]
  t_value <- model_summary$coefficients[2, 3]
  p_value <- model_summary$coefficients[2, 4]
  conf_low <- model_confint[2, 1]
  conf_high <- model_confint[2, 2]
  r_squared <- model_summary$r.squared * 100
  
  cat("========================================\n")
  cat("        REGRESSION SUMMARY -", stock_name, "\n")
  cat("========================================\n")
  cat(sprintf("%-25s: %.4f\n", "Beta", beta))
  cat(sprintf("%-25s: %.2f\n", "t-value", t_value))
  cat(sprintf("%-25s: %.4g\n", "p-value", p_value))
  cat(sprintf("%-25s: [%.4f , %.4f]\n", "95% Confidence Interval", conf_low, conf_high))
  cat(sprintf("%-25s: %.2f%%\n", "R-squared", r_squared))
  cat("========================================\n\n")
}

weights <- c(0.30, 0.20, 0.50)
portfolio_returns <- returns_aapl * weights[1] + returns_tsla * weights[2] + returns_msft * weights[3]

print_regression_summary("AAPL", returns_aapl, portfolio_returns)
print_regression_summary("TSLA", returns_tsla, portfolio_returns)
print_regression_summary("MSFT", returns_msft, portfolio_returns)

```
The table above clearly presents the influence of AAPL, TSLA, and MSFT on the portfolio returns, along with the statistical reliability of these effects.

AAPL and MSFT show strong and statistically significant relationships with the portfolio returns. Their beta values, around 0.85-0.86, indicate that these stocks contribute stabilizing effects to the portfolio’s performance. MSFT, in particular, stands out with the highest explanatory power (77.46%), making it the most aligned stock with the portfolio performance.

TSLA, with a high beta of 1.62, is identified as the most influential stock in driving portfolio movements. This highlights TSLA's high volatility and risk, but also its high return potential. However, its lower R² (59.11%) compared to AAPL and MSFT suggests that TSLA carries additional, less predictable risk factors beyond the portfolio’s general movements.

All results are highly statistically significant (p < 0.001), and the narrow and positive confidence intervals further confirm the robustness and reliability of the estimates.


This table demonstrates that MSFT and AAPL act as stabilizers, contributing to portfolio consistency, while TSLA drives both risk and return dynamics.
For a balanced portfolio, the weight of TSLA should be carefully managed to control overall risk, while AAPL and MSFT provide stable and reliable performance contributions.


--------------------------------------------------------------------------------

We can prove this by calculating standard deviation both for diversified investment and single one and compare them. As we know, standard deviation considered to be a "Risk Marker", so we expect diversified portfolio to have lower standard deviation score.


```{r}

portfolio_returns <- (returns_aapl + returns_msft + returns_tsla) / 3

cat("Standard Deviation of AAPL:", sd(returns_aapl), "\n")
cat("Standard Deviation of MSFT:", sd(returns_msft), "\n")
cat("Standard Deviation of TSLA:", sd(returns_tsla), "\n")
cat("Standard Deviation of Diversified Portfolio:", sd(portfolio_returns), "\n")
```
As you can see, our diversified portfolio has 2% of Standard Deviation, meanwhile, AAPL and MSFT have 1.94% and 1.83% respectively. That means 2 things. 1 - I was wrong, Standard deviation of our portfolio is higher. 2 - AAPL and MSFT itself more safe asset to have. 

Why then Mr. Markowitz was so desperate about diversification? 
And the answer is - return. Let me explain.

When we combine these three stocks into an equally weighted diversified portfolio, the portfolio’s standard deviation is 2.17%, which is lower than Tesla’s individual risk, but slightly higher than Apple’s or Microsoft’s risk.

This result demonstrates that diversification reduces the overall impact of the riskiest asset in the portfolio. Even though the portfolio still carries some risk, the extreme fluctuations of Tesla are balanced out by the relative stability of Apple and Microsoft.

Moreover, the potential return of the diversified portfolio remains attractive, since it still benefits from Tesla’s higher return potential while reducing its extreme downside risk.

Therefore, this example illustrates why diversification makes sense in practice: it helps to lower risk while preserving opportunities for higher returns.

Is simple terms, as we want our portfolio to grow, we can invest in risky assets to gain more and still consider our portfolio to be safe, using this.

Let me demonstrate it, using the following chart:


```{r}

mean_portfolio <- mean(portfolio_returns)
sd_portfolio <- sd(portfolio_returns)

metrics <- data.frame(
  Asset = c("Apple", "Microsoft", "Tesla", "Diversified Portfolio"),
  Mean_Return = c(mean_return_aapl, mean_return_msft, mean_return_tsla, mean_portfolio),
  Standard_Deviation = c(sd_aapl, sd_msft, sd_tsla, sd_portfolio)
)

print(metrics)

plot(metrics$Standard_Deviation, metrics$Mean_Return,
     xlab = "Risk (Standard Deviation)",
     ylab = "Return (Mean Daily Return)",
     main = "Risk-Return Comparison",
     pch = 19, col = c("blue", "green", "red", "black"),
     xlim = c(0, max(metrics$Standard_Deviation) * 1.1),
     ylim = c(0, max(metrics$Mean_Return) * 1.1))
text(metrics$Standard_Deviation, metrics$Mean_Return, labels = metrics$Asset, pos = 4)
```
The Risk-Return Comparison chart illustrates how diversification helps to balance risk and return.

We can see that Tesla provides the highest average return (0.28%) but comes with the highest risk (4.06% standard deviation). On the other hand, Apple and Microsoft offer lower risk (around 1.8–1.9%) but also lower returns (around 0.11–0.14%).

The diversified portfolio, which combines all three stocks equally, achieves a higher return (0.18%) than Apple and Microsoft individually, while maintaining a moderate risk (2.17%), significantly lower than Tesla’s standalone risk.

This shows that diversification allows us to benefit from the growth potential of riskier assets like Tesla while keeping the overall risk at an acceptable level thanks to the stabilizing effect of safer assets like Apple and Microsoft.

In other words, diversification does not eliminate risk entirely, but it smooths the extremes, providing a more balanced and resilient portfolio that preserves the opportunity for higher returns without fully exposing the investor to the risks of any single stock.

To strengthen the analysis, we conducted two additional statistical tests:
	•	T-Test: This test was used to check whether the difference in returns between Tesla and Apple is statistically significant. The results confirmed that Tesla’s returns are not significantly higher than Apple’s, with a p-value above 0.05, supporting the conclusion that Tesla offers nearly same potential returns but at a higher risk.(Askim, please check. Maybe I calculated it wrong. It shouldn't be the same)
	
	
```{r}
t_test_result <- t.test(as.vector(returns_tsla), as.vector(returns_aapl))
print(t_test_result)
```

--------------------------------------------------------------------	












	
	
--------------------------------------------------------------------	
	
	•	Linear Regression: A regression analysis between Tesla’s returns and the diversified portfolio’s returns revealed a positive relationship. This indicates that Tesla’s performance has a measurable influence on the portfolio’s overall return, contributing to both its higher return and higher volatility. This supports the idea that adding a riskier asset like Tesla can boost portfolio performance while still maintaining a balanced risk profile thanks to diversification.
	
```{r}
# Линейная регрессия доходности Tesla против доходности портфеля
regression_model <- lm(returns_tsla ~ portfolio_returns)

# Вывод результата
summary(regression_model)
```

The linear regression results show a strong and statistically significant positive relationship between the returns of Tesla and the returns of the diversified portfolio.

Since the p-value is nearly 0, the probability of the result being an accident is extremely low. We can trust the result.

The coefficient of 1.65 indicates that Tesla’s returns amplify the portfolio’s movements, meaning Tesla behaves like a high-beta asset, increasing portfolio returns when the portfolio performs well, but also increasing losses when the portfolio performs poorly (higher volatility). That means that when our portfolio grows 1%, Tesla grows 1.65%.

With an R-squared of 77.8%, the model explains a large portion of Tesla’s return variability, confirming that Tesla’s performance is closely related to the portfolio’s overall dynamics. This reinforces the idea that adding Tesla to a diversified portfolio can boost returns, but it also makes the portfolio more sensitive to market movements.
⸻



---
https://www.thestreet.com/apple/stock/apple-vs-tesla-which-growth-stock-to-own#:~:text=Apple%20vs,vs.%20AAPL%27s%2040

---
https://www.thestreet.com/apple/stock/apple-vs-tesla-which-growth-stock-to-own#:~:text=Apple%20vs,vs.%20AAPL%27s%2040

https://www.investopedia.com/articles/investing/071113/breaking-down-geometric-mean.asp

https://www.thestreet.com/retirement-daily/your-money/testing-chatgpt-arithmetic-vs-geometric-returns

---

https://corporatefinanceinstitute.com/resources/career-map/sell-side/capital-markets/harry-markowitz/

